Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-09-12 manuscript.Rmd
add apa.csl to dependencies

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: false
    number_sections: false
header-includes:
   - \usepackage{libertine}
fontsize: 11pt
linestretch: 1.2
geometry: "left=3.9cm, right=3.3cm, top=2.5cm, bottom=3cm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
csl: apa.csl
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
  packages:
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
  tlmgr:
    - pgf
    - preview
    - libertine
  apt:
    - git
    - rsync
    - curl
    - inkscape
---

>>>>

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: false
    number_sections: false
header-includes:
   - \usepackage{libertine}
fontsize: 11pt
linestretch: 1.2
geometry: "left=3.9cm, right=3.3cm, top=2.5cm, bottom=3cm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
csl: apa.csl
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
    - apa.csl
  packages:
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
  tlmgr:
    - pgf
    - preview
    - libertine
  apt:
    - git
    - rsync
    - curl
    - inkscape
---
